Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-05-13 hotstorage13/background.tex
revised
give reasoning on why we want to avoid dedicated dedup nodes

%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. Only raw access information at disk block level are provided. 
%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%only a very small slice of cluster resource can be used for the backup purpose.

%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.
Offline deduplication is used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%,NGmiddleware2011}.
%Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper}
%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
Several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
Still such methods use  a significant amount of memory resource for filtering and caching.
%NG et al.~\cite{ NGmiddleware2011}  use
%a related filtering technique for integrating deduplication in Linux  file system and the memory
%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%These are segments that share many chunk IDs with the incoming segment with high probability.
The approximation techniques are studied in~\cite{extreme_binning09,WeiZhangIEEE}  
%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%lookup  
In comparison, this paper focuses on  full deduplication without approximation.

>>>>

%In a virtualized cloud environment such as ones provided by Amazon EC2\cite{AmazonEC2} and Alibaba Aliyun\cite{Aliyun}, 
At a cloud cluster node, each instance of a guest operating system runs on a virtual machine, accessing virtual hard disks 
represented as virtual disk image files in the host operating system.
For VM snapshot backup, file-level semantics are normally not provided.
Snapshot operations take place at the virtual device driver level, which means no fine-grained file system metadata can be used to determine the changed data. 
%Only raw access information at disk block level are provided. 
%Each physical machine hosts many VMs and petabytes of data in a cloud cluster need a frequent  backup. 
%Ideally speaking, snapshot backup must not affect the normal cloud service, which means that 
%only a very small slice of cluster resource can be used for the backup purpose.

%The previous work for storage backup has extensively used  data deduplication techniques can eliminate redundancy globally among different files from different users.
Backup systems have been developed to use content fingerprints to identify duplicate
content~\cite{venti02,Rhea2008}.
Offline deduplication is used in ~\cite{EMC,NetAppOffline} to remove previously written duplicate blocks during idle time.
%,NGmiddleware2011}.
%Today's commercial data backup systems (e.g. from EMC and NetApp)
%\cite{emc_avamar}\cite{datadomain_whitepaper}
%use a variable-size chunking algorithm to detect duplicates in file data~\cite{similar94,hydrastor09}.
Several techniques have been proposed to speedup searching of duplicate
fingerprints. For example, the data domain method ~\cite{bottleneck08} 
uses  an in-memory Bloom filter and a prefetching cache for data blocks  which may be
accessed.  An improvement to this work with parallelization is in ~\cite{MAD210,DEBAR}.
%Still such methods use a significant amount of memory resource for filtering and caching.
Such methods use dedicated nodes for deduplication, which add cost to cloud infrastructure and is less scalable.
%NG et al.~\cite{ NGmiddleware2011}  use
%a related filtering technique for integrating deduplication in Linux  file system and the memory
%consumed is up to 2GB for a single machine. That is still too big in our context discussed below.
%Lillibridge et al.~\cite{sparseindex09} break list of chunks
%into large segments, the chunk IDs in each incoming segment are sampled and the segment is
%deduplicated by comparing with the chunk IDs of only a few carefully selected backed up segments.
%These are segments that share many chunk IDs with the incoming segment with high probability.
The approximation techniques are studied in~\cite{extreme_binning09,Guo2011,WeiZhangIEEE}  
%Deepavali et al.~\cite{extreme_binning09} and Zhang et al.~\cite{WeiZhangIEEE}  
to reduce memory requirement with a tradeoff of the reduced deduplication ratio.
%use fingerprint-based file similarity  and group similar files into the same physical location (bins) to deduplicate against each other.
%That leads  to a smaller amount of memory usage for storing meta data in fingerprint
%lookup  
In comparison, this paper focuses on  full deduplication without approximation.
